Calculating Entropies With Nested Sampling

### 2017-02-04 paper/ms.tex
Waxing about precisional questions

>>>>

\appendix
\section{Precisional questions}

The central issue about the value of a parameter $\x$ asks
``what is the value of $\x$, precisely?''. However, in practice we often
don't need or want to know $\x$ to arbitrary precision. Using the central
issue can also lead to counterintuitive results if you don't keep its
definition in mind. For example, suppose $\x$ could take any integer value
from 1 to 1 billion. If we learned that the last digit of $\x$ was a 9, we
will have ruled out nine tenths of the possibilities, and therefore obtained
a lot of information about the central issue. However, in many applications
this ``information'' would be basically useless.

The reason is that we often want to ask a slightly different question.
For example, suppose we want to know the value of $\x$ to within a tolerance
of $\pm 5$. The following statements would resolve the issue:
\begin{itemize}
\item $\x \in \{1, ..., 10\}$ and anything that implies it
\item $\x \in \{2, ..., 11\}$ and anything that implies it
...
\end{itemize}
